\bf Comparing the Power of Plot Designs to Reveal Correlation

### 2016-01-05 paper/paper.Rnw
Changes

\begin{figure}[htbp]
  \centering
<<lineup.example, dependson='setup', fig.width=6, fig.height=6, out.width='0.7\\textwidth', echo=FALSE, warning=FALSE, message=FALSE>>=
set.seed(1234)
a <- gen_true_data(24, 0.95)
td <- gather(a, variable, value, c(X1, X2))
b <- gen_null(24)
nd_l <- gather(b, variable, value, c(X1, X2))
pos <- 7
td <- data.frame(.n=rep(pos, nrow(td)), td)
lg <- nd_l$.n < pos
nd_l1 <- data.frame(.n=nd_l$.n[lg], t=nd_l$t[lg], variable=nd_l$variable[lg], 
                    value=nd_l$value[lg])
nd_l2 <- data.frame(.n=nd_l$.n[!lg], t=nd_l$t[!lg], variable=nd_l$variable[!lg], 
                    value=nd_l$value[!lg])
nd_l2$.n <- nd_l2$.n + 1
d <- rbind(nd_l1, td, nd_l2)

@@

\begin{figure}[htbp]
  \centering
<<smoothing, dependson='setup', fig.width=6, fig.height=6, out.width='0.7\\textwidth', echo=FALSE, warning=FALSE, message=FALSE>>=
set.seed(123)
uns <- gen_true_data(96, 0.8)
uns_l <- gather(uns, variable, value, -t)
p1a <- ggplot(data=uns_l, aes(x=t, y=value, colour=variable)) + geom_line() +labs(title="Unsmoothed Overlaid Lines") +
    theme(axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          legend.position="none")
p3a <- ggplot(data=uns, aes(x=X1, y=X2)) + geom_point()+ labs(title="Unsmoothed Scatterplot)") +
    theme(aspect.ratio=1, axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          legend.position="none")

@@

\begin{figure}[htbp]
  \centering
<<designs, dependson='setup', fig.width=6, fig.height=6, out.width='0.7\\textwidth', echo=FALSE, warning=FALSE, message=FALSE>>=
set.seed(101)
a <- gen_true_data(24, 0.95)
b <- gen_true_data(24, -0.95)
a_l <- gather(a, variable, value, -t)
b_l <- gather(b, variable, value, -t)
p1b <- ggplot(data=a_l, aes(x=t, y=value, colour=variable)) + geom_line() + labs(title="Overlaid line graph") +
      theme(axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          legend.position="none")
p2b <- ggplot(data=b_l, aes(x=t, y=value, colour=variable)) + geom_line() + labs(title="Overlaid line graph") +
      theme(axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          legend.position="none")
p3b <- ggplot(data=a, aes(x=X1, y=X2)) + geom_point() + labs(title="Scatterplot") +
      theme(aspect.ratio=1, axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          legend.position="none")
p4b <- ggplot(data=b, aes(x=X1, y=X2)) + geom_point() + labs(title="Scatterplot") +
      theme(aspect.ratio=1, axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          legend.position="none")
grid.arrange(p1b, p2b, p3b, p4b, ncol=2)
@
  \label{designs}
  \caption{The same two data sets in both plot designs. t=24, correlation (left) = 0.946, correlation (right) = -0.943}
\end{figure}

@@

\begin{figure}[htbp]
 \centering
<<results, dependson='setup', fig.width=6, fig.height=8, out.width='0.7\\textwidth', echo=FALSE, warning=FALSE>>=
Turk <- mutate(Turk, plot = ifelse(test_param =="line", "Overlaid Lines", "Scatterplot"), 
               sign=ifelse(correlation > 0, 1, 0), smoothed=ifelse(smoothed=="yes", 1, 0))
#ggplot(data=subset(Turk, smoothed==0), aes(x=correlation, y=percent, colour=plot)) + geom_smooth() + geom_point() + facet_grid(n~.) + scale_colour_discrete(name = "Plot Design") +  labs(title="Unsmoothed Plot Accuracy", y="Percent Correct", x="True Plot Correlation")
ggplot(data=Turk, aes(x=correlation, y=percent, colour=plot)) + geom_smooth(se=F) + geom_point() + facet_grid(n~smoothed) + 
  scale_colour_discrete(name = "Plot Design") + labs(title="Observed Data", y="Percent Correct", x="Correlation") +
  theme(legend.position="bottom")
@
  \label{results}
  \caption{Response accuracy for unsmoothed data, broken by unsmoothed (left), smoothed (right) and sample size. The dots are data points, the lines represent a naive model average fit. Both plot designs have similar performance for positively correlated data, however the overlaid line graphs are particularly weak at revealing negative correlation.}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
<<powerdiff, dependson='results', fig.width=6, fig.height=8, out.width='0.7\\textwidth', echo=FALSE>>=
Turk$correct <- Turk$percent*Turk$attempt
Turk$r <- round(Turk$correlation, 1)
#Turk.line <- subset(Turk, test_param=="line")
#Turk.scatter <- subset(Turk, test_param=="scatter")
prop <- Turk[order(Turk$r, Turk$n, Turk$smoothed),c("smoothed", "n", "attempt", "correct", "r", "plot")]
prop <- summarise(group_by(prop, smoothed, n, r), l.attempt=sum(ifelse(plot=="Overlaid Lines", attempt, 0)),
                                                  l.correct=sum(ifelse(plot=="Overlaid Lines", correct, 0)),
                                                  s.attempt=sum(ifelse(plot=="Scatterplot", attempt, 0)),
                                                  s.correct=sum(ifelse(plot=="Scatterplot", correct, 0)))
#Turk.line <- Turk.line[order(Turk.line$r, Turk.line$n, Turk.line$smoothed),c("smoothed", "n", "attempt", "correct", "r")]
#Turk.line <- summarise(group_by(Turk.line, smoothed, n, r, test_param), sum(attempt), sum(correct))
#Turk.scatter <- Turk.scatter[order(Turk.scatter$r, Turk.scatter$n, Turk.scatter$smoothed),c("smoothed", "n", "attempt", "correct", "r")]
#Turk.scatter <- summarise(group_by(Turk.scatter, smoothed, n, r), sum(attempt), sum(correct))
#colnames(Turk.scatter) <- c("smoothed", "n", "r", "s.attempt", "s.correct")
#colnames(Turk.line) <- c("smoothed", "n", "r", "l.attempt", "l.correct")
#prop <- cbind(Turk.line, Turk.scatter[4:5])
prop <- mutate(prop, l.adj = (l.correct+1)/(l.attempt+1), s.adj = (s.correct+1)/(s.attempt+1),
               df = s.attempt + l.attempt - 1, difference=s.adj-l.adj, t = qt(0.975, df),
               upper = difference + t*sqrt(s.adj*(1-s.adj)/s.attempt+l.adj*(1-l.adj)/l.attempt),
               lower = difference - t*sqrt(s.adj*(1-s.adj)/s.attempt+l.adj*(1-l.adj)/l.attempt))
ggplot(data=prop) + geom_errorbar(aes(x=r, ymax=upper, ymin=lower)) + geom_point(aes(x=r, y=difference)) +
        geom_hline(aes(yint=0, colour="red")) + labs(title="Difference in Power", x="Correlation", y="Scatterplot Advantage") + facet_grid(n~smoothed)
@
 \label{powerdiff}
 \caption{The difference in estimated power (scatter plot power minus overlaid line power) to reveal the true plot by smoothness and sample size with a 95\% confidence interval. The red line indicates the point where both plot designs are equally powerful while values above this line indicate that the scatter plot is more powerful than the overlaid line graph. Again, the largest advantage difference appears in negative correlation, where the scatter plot is more powerful.}
\end{figure}

\begin{figure}[htbp]
  \centering
<<samplesize, dependson='powerdiff', fig.width=6, fig.height=8, out.width='0.7\\textwidth', echo=FALSE>>=
ggplot(data=subset(Turk, smoothed==0), aes(x=correlation, y=percent, colour=factor(n))) + geom_smooth(se=F) + geom_point() + facet_grid(plot~.) + scale_colour_discrete(name = "Sample size") +  labs(title="Effect of sample size, with unsmoothed data", y="Percent Correct", x="Correlation") + theme(legend.position="bottom")
@
 \label{samplesize}
 \caption{Replotting figure~\ref{results} to highlight the effects of changes in sample size of unsmoothed data. The scatter plot appears to universaly benefit from increased sample sizes but the overlaid lines only see a benefit in positive correlation.}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
<<time, dependson='setup', fig.width=6, fig.height=6, out.width='0.7\\textwidth', echo=FALSE>>=
full <- mutate(full, sign = ifelse(correlation >= 0, 1, 0), n24 = ifelse(n ==24, 1, 0), n48 = ifelse(n ==48,  1, 0), n96 = ifelse(n ==96, 1, 0), plot = ifelse(test_param ==1, "Overlaid Lines", "Scatterplot"))
time <- data.frame(plot=full$plot, time=full$log_time, correct=full$correct, rsgn=full$sign)
#ggplot(data=time, aes(x=time, fill=factor(correct))) +geom_bar(stat="bin") + facet_grid(~plot) +labs(x="Log(Time) Taken", y=element_blank()) + scale_fill_discrete(name = "Correct")
time$rsgn <- factor(time$rsgn, labels=c("r -","r +"))
tm <- summarise(group_by(time, correct, plot, rsgn), m=mean(time))
t1 <- ggplot(data=subset(time, correct==0), aes(x=time)) + geom_histogram(binwidth=0.5) + 
  geom_vline(data=subset(tm, correct==0), aes(xintercept = m), color="red") +
  facet_grid(plot~rsgn) + labs(title="Did not detect", x="Log(Time) Taken", y=element_blank())  
t2 <- ggplot(data=subset(time, correct==1), aes(x=time)) + geom_histogram(binwidth=0.5) + 
  geom_vline(data=subset(tm, correct==1), aes(xintercept = m), color="red") +
  facet_grid(plot~rsgn) + labs(title="Detected", x="Log(Time) Taken", y=element_blank())  
grid.arrange(t1, t2, ncol=2, top = "Log(Time) by plot design, true plot correlation and detection")
@
  \label{time} 
  \caption{Histograms of log time taken to make a decision. r+ and r- indicate the sign of true plot correlation. The vertical red line is the average time of the particular group. On average scatter plots are faster and the true plot is detected more often, with r-.}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
<<confidence, dependson='time', fig.width=6, fig.height=6, out.width='0.7\\textwidth', echo=FALSE>>=
conf <- data.frame(plot=full$plot, conf=full$conf_level, correct=full$correct, rsgn=full$sign)
conf$rsgn <- factor(conf$rsgn, labels=c("r -","r +"))
cm <- summarise(group_by(conf, correct, plot, rsgn), m=mean(conf))
c1 <- ggplot(data=subset(conf, correct==0), aes(x=conf)) + geom_histogram(binwidth=1) + 
  geom_vline(data=subset(cm, correct==0), aes(xintercept = m), color="red") +
  facet_grid(plot~rsgn) + labs(title="Did not detect", x="Confidence", y=element_blank())  
c2 <- ggplot(data=subset(conf, correct==1), aes(x=conf)) + geom_histogram(binwidth=1) + 
  geom_vline(data=subset(cm, correct==1), aes(xintercept = m), color="red") +
  facet_grid(plot~rsgn) + labs(title="Detected", x="Confidence", y=element_blank())  
grid.arrange(c1, c2, ncol=2, top = "Confidence by plot design, true plot correlation and detection")
@
  \label{confidence} 
  \caption{Histograms of reported confidence levels. 1 - Low, 5 - High. Detection had a minor detrimental impact on confidence, whilst time taken increased it. There was no statistically significant difference on confidence level between plot designs.}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
<<confidence2, dependson='time', fig.width=6, fig.height=6, out.width='0.7\\textwidth', echo=FALSE, warning=FALSE>>=
full$subj_id <- factor(full$ip_address, labels=1:207)
y <- data.frame(table(full$subj_id))
keep2 <- y$Var1[y$Freq>9]
sub <- filter(full, subj_id %in% keep2)
sub <- select(sub, conf_level, correlation, test_param, smoothed, n, correct, sign, plot, subj_id) #c(7, 15, 16, 17, 20, 27)]
#sub <- summarise(group_by(sub, subj_id), correct = sum(correct), conf=mean(conf_level))
#sub <- merge(sub, y, by.x="subj_id", by.y="Var1")
#sub <- mutate(sub, prop = correct/Freq)
qplot(correlation, 6-conf_level, data=sub, alpha=I(0.1)) + 
  geom_smooth(method="loess") + 
  facet_grid(n~plot+smoothed) +
  labs(x = "Correlation", y = "Confidence (5=High, 1=Low)")
@
  \label{confidence2}
  \caption{Individual subject accuracy versus subject average confidence. There does not appear to be any relationship between the two.}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
<<pins, dependson='samplesize', fig.width=6, fig.height=10, out.width='0.7\\textwidth', echo=FALSE, warning=FALSE>>=
# correl <- read.csv("correlations.csv") # You have already read this
count.setup <- select(full, pic_id, response_0, actual_location, 
              test_param, smoothed, n)
count.setup$response_0 <- as.character(count.setup$response_0) #full[,c(5, 6, 10, 15, 16, 17)]
# Need to use the tidyr commands instead of cSplit
# Here's where we will need to make some changes to incorporate the multiple picks
#pin <- pin %>% transform(response_0= strsplit(as.character(response_0), ",")) %>% unnest(response_0)
#pin$response_0 <- separate(pin, response_0, "response_0", sep=",", extra="drop")
count.setup$choice <- separate(count.setup, response_0, c("choice", "l1", "l2"), ",", extra="drop")$choice
count.setup$choice[str_detect(count.setup$actual_location, count.setup$response_0)] <- 
  count.setup$actual_location[str_detect(count.setup$actual_location, count.setup$response_0)]
                         #as.integer(pin$response_0)
counts <- data.frame(table(count.setup$pic_id, count.setup$choice))
counts$Var1 <- as.numeric(as.character(counts$Var1))
counts$Var2 <- as.numeric(as.character(counts$Var2))
colnames(counts) <- c("lineup", "plot", "count")
pin <- merge(counts, Turk[-19], by.x="lineup", by.y="pic_id")
pin <- select(pin, lineup, plot, count, smoothed, true_pos, n, test_param, r)#pin[,c(1, 2, 3, 12, 13, 15, 11, 20)]
pin$r <- factor(pin$r)
colnames(pin) <- c("lineup", "plot", "count", "smoothed", "true_pos", "n", "design", "r")
pin <- mutate(pin, design=ifelse(design=="scatter", "Scatterplot", "Overlaid Lines"))#, smoothed=ifelse(smoothed=="no", 0, 1))
pin$base <- 0
pin$Correlation <- diag(as.matrix(correl[pin$lineup, (pin$plot+2)]))
pin <- mutate(pin, true = ifelse(plot==true_pos, "True plot", "Null plot"), percent = count/attempt)
#pin <- merge(pin, Turk[,c(2, 16)], by.x = "lineup", by.y = "pic_id")
pin.a <- ggplot(data=filter(pin, smoothed==0 & design == "Scatterplot")) + geom_errorbar(aes(x=Correlation, ymin=base, ymax=percent, colour=true)) +
       geom_point(aes(x=Correlation, y=percent, colour=true)) + coord_fixed() + facet_grid(n~r) + labs(title="Unsmoothed Scatterplot", y="Percent Chosen") + theme(legend.position="none")
pin.b <- ggplot(data=subset(pin, smoothed==1 & design == "Scatterplot")) + geom_errorbar(aes(x=Correlation, ymin=base, ymax=percent, colour=true)) +
  geom_point(aes(x=Correlation, y=percent, colour=true)) + coord_fixed()  + facet_grid(n~r) + labs(title="Smoothed Scatterplot", y="Percent Chosen") + theme(legend.position="none")
pin.c <- ggplot(data=subset(pin, smoothed==0 & design == "Overlaid Lines")) + geom_errorbar(aes(x=Correlation, ymin=base, ymax=percent, colour=true)) +
  geom_point(aes(x=Correlation, y=percent, colour=true)) + coord_fixed()  + facet_grid(n~r) + labs(title="Unsmoothed Overlaid Lines", y="Percent Chosen") + theme(legend.position="none")
pin.d <- ggplot(data=subset(pin, smoothed==1 & design == "Overlaid Lines")) + geom_errorbar(aes(x=Correlation, ymin=base, ymax=percent, colour=true)) +
  geom_point(aes(x=Correlation, y=percent, colour=true)) + coord_fixed()  + facet_grid(n~r) + labs(title="Smoothed Overlaid Lines", y="Percent Chosen") + theme(legend.position="none")
grid.arrange(pin.a, pin.b, pin.c, pin.d, ncol=1)
@

>>>>

\begin{figure}[htbp]
  \centering
<<lineup.example, dependson='setup', fig.width=6, fig.height=6, out.width='0.7\\textwidth', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE>>=
set.seed(1234)
a <- gen_true_data(24, 0.95)
td <- gather(a, variable, value, c(X1, X2))
b <- gen_null(24)
nd_l <- gather(b, variable, value, c(X1, X2))
pos <- 7
td <- data.frame(.n=rep(pos, nrow(td)), td)
lg <- nd_l$.n < pos
nd_l1 <- data.frame(.n=nd_l$.n[lg], t=nd_l$t[lg], variable=nd_l$variable[lg], 
                    value=nd_l$value[lg])
nd_l2 <- data.frame(.n=nd_l$.n[!lg], t=nd_l$t[!lg], variable=nd_l$variable[!lg], 
                    value=nd_l$value[!lg])
nd_l2$.n <- nd_l2$.n + 1
d <- rbind(nd_l1, td, nd_l2)

@@

\begin{figure}[htbp]
  \centering
<<smoothing, dependson='setup', fig.width=6, fig.height=6, out.width='0.7\\textwidth', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE>>=
set.seed(123)
uns <- gen_true_data(96, 0.8)
uns_l <- gather(uns, variable, value, -t)
p1a <- ggplot(data=uns_l, aes(x=t, y=value, colour=variable)) + geom_line() +labs(title="Unsmoothed Overlaid Lines") +
    theme(axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          legend.position="none")
p3a <- ggplot(data=uns, aes(x=X1, y=X2)) + geom_point()+ labs(title="Unsmoothed Scatterplot)") +
    theme(aspect.ratio=1, axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          legend.position="none")

@@

\begin{figure}[htbp]
  \centering
<<designs, dependson='setup', fig.width=6, fig.height=6, out.width='0.7\\textwidth', echo=FALSE, warning=FALSE, message=FALSE, error=FALSE>>=
set.seed(101)
a <- gen_true_data(24, 0.95)
b <- gen_true_data(24, -0.95)
a_l <- gather(a, variable, value, -t)
b_l <- gather(b, variable, value, -t)
p1b <- ggplot(data=a_l, aes(x=t, y=value, colour=variable)) + geom_line() + labs(title="Overlaid line graph") +
      theme(axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          legend.position="none")
p2b <- ggplot(data=b_l, aes(x=t, y=value, colour=variable)) + geom_line() + labs(title="Overlaid line graph") +
      theme(axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          legend.position="none")
p3b <- ggplot(data=a, aes(x=X1, y=X2)) + geom_point() + labs(title="Scatterplot") +
      theme(aspect.ratio=1, axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          legend.position="none")
p4b <- ggplot(data=b, aes(x=X1, y=X2)) + geom_point() + labs(title="Scatterplot") +
      theme(aspect.ratio=1, axis.title.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          legend.position="none")
grid.arrange(p1b, p2b, p3b, p4b, ncol=2)
@
  \label{designs}
  \caption{The same two data sets in both plot designs. t=24, correlation (left) = 0.946, correlation (right) = -0.943}
\end{figure}

@@

\begin{figure}[htbp]
 \centering
<<results, dependson='setup', fig.width=6, fig.height=8, out.width='0.7\\textwidth', echo=FALSE, warning=FALSE, error=FALSE, message=FALSE>>=
Turk <- mutate(Turk, plot = ifelse(test_param =="line", "Overlaid Lines", "Scatterplot"), 
               sign=ifelse(correlation > 0, 1, 0), smoothed=ifelse(smoothed=="yes", 1, 0))
#ggplot(data=subset(Turk, smoothed==0), aes(x=correlation, y=percent, colour=plot)) + geom_smooth() + geom_point() + facet_grid(n~.) + scale_colour_discrete(name = "Plot Design") +  labs(title="Unsmoothed Plot Accuracy", y="Percent Correct", x="True Plot Correlation")
ggplot(data=Turk, aes(x=correlation, y=percent, colour=plot)) + geom_smooth(se=F) + geom_point() + facet_grid(n~smoothed) + 
  scale_colour_discrete(name = "Plot Design") + labs(title="Observed Data", y="Percent Correct", x="Correlation") +
  theme(legend.position="bottom")
@
  \label{results}
  \caption{Response accuracy for unsmoothed data, broken by unsmoothed (left), smoothed (right) and sample size. The dots are data points, the lines represent a naive model average fit. Both plot designs have similar performance for positively correlated data, however the overlaid line graphs are particularly weak at revealing negative correlation.}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
<<powerdiff, dependson='results', fig.width=6, fig.height=8, out.width='0.7\\textwidth', echo=FALSE, error=FALSE, message=FALSE, warning=FALSE>>=
Turk$correct <- Turk$percent*Turk$attempt
Turk$r <- round(Turk$correlation, 1)
#Turk.line <- subset(Turk, test_param=="line")
#Turk.scatter <- subset(Turk, test_param=="scatter")
prop <- Turk[order(Turk$r, Turk$n, Turk$smoothed),c("smoothed", "n", "attempt", "correct", "r", "plot")]
prop <- summarise(group_by(prop, smoothed, n, r), l.attempt=sum(ifelse(plot=="Overlaid Lines", attempt, 0)),
                                                  l.correct=sum(ifelse(plot=="Overlaid Lines", correct, 0)),
                                                  s.attempt=sum(ifelse(plot=="Scatterplot", attempt, 0)),
                                                  s.correct=sum(ifelse(plot=="Scatterplot", correct, 0)))
#Turk.line <- Turk.line[order(Turk.line$r, Turk.line$n, Turk.line$smoothed),c("smoothed", "n", "attempt", "correct", "r")]
#Turk.line <- summarise(group_by(Turk.line, smoothed, n, r, test_param), sum(attempt), sum(correct))
#Turk.scatter <- Turk.scatter[order(Turk.scatter$r, Turk.scatter$n, Turk.scatter$smoothed),c("smoothed", "n", "attempt", "correct", "r")]
#Turk.scatter <- summarise(group_by(Turk.scatter, smoothed, n, r), sum(attempt), sum(correct))
#colnames(Turk.scatter) <- c("smoothed", "n", "r", "s.attempt", "s.correct")
#colnames(Turk.line) <- c("smoothed", "n", "r", "l.attempt", "l.correct")
#prop <- cbind(Turk.line, Turk.scatter[4:5])
prop <- mutate(prop, l.adj = (l.correct+1)/(l.attempt+1), s.adj = (s.correct+1)/(s.attempt+1),
               df = s.attempt + l.attempt - 1, difference=s.adj-l.adj, t = qt(0.975, df),
               upper = difference + t*sqrt(s.adj*(1-s.adj)/s.attempt+l.adj*(1-l.adj)/l.attempt),
               lower = difference - t*sqrt(s.adj*(1-s.adj)/s.attempt+l.adj*(1-l.adj)/l.attempt))
ggplot(data=prop) + geom_errorbar(aes(x=r, ymax=upper, ymin=lower)) + geom_point(aes(x=r, y=difference)) +
        geom_hline(aes(yint=0, colour="red")) + labs(title="Difference in Power", x="Correlation", y="Scatterplot Advantage") + facet_grid(n~smoothed)
@
 \label{powerdiff}
 \caption{The difference in estimated power (scatter plot power minus overlaid line power) to reveal the true plot by smoothness and sample size with a 95\% confidence interval. The red line indicates the point where both plot designs are equally powerful while values above this line indicate that the scatter plot is more powerful than the overlaid line graph. Again, the largest advantage difference appears in negative correlation, where the scatter plot is more powerful.}
\end{figure}

\begin{figure}[htbp]
  \centering
<<samplesize, dependson='powerdiff', fig.width=6, fig.height=8, out.width='0.7\\textwidth', echo=FALSE, error=FALSE, message=FALSE, warning=FALSE>>=
ggplot(data=subset(Turk, smoothed==0), aes(x=correlation, y=percent, colour=factor(n))) + geom_smooth(se=F) + geom_point() + facet_grid(plot~.) + scale_colour_discrete(name = "Sample size") +  labs(title="Effect of sample size, with unsmoothed data", y="Percent Correct", x="Correlation") + theme(legend.position="bottom")
@
 \label{samplesize}
 \caption{Replotting figure~\ref{results} to highlight the effects of changes in sample size of unsmoothed data. The scatter plot appears to universaly benefit from increased sample sizes but the overlaid lines only see a benefit in positive correlation.}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
<<time, dependson='setup', fig.width=6, fig.height=6, out.width='0.7\\textwidth', echo=FALSE, error=FALSE, message=FALSE, warning=FALSE>>=
full <- mutate(full, sign = ifelse(correlation >= 0, 1, 0), n24 = ifelse(n ==24, 1, 0), n48 = ifelse(n ==48,  1, 0), n96 = ifelse(n ==96, 1, 0), plot = ifelse(test_param ==1, "Overlaid Lines", "Scatterplot"))
time <- data.frame(plot=full$plot, time=full$log_time, correct=full$correct, rsgn=full$sign)
#ggplot(data=time, aes(x=time, fill=factor(correct))) +geom_bar(stat="bin") + facet_grid(~plot) +labs(x="Log(Time) Taken", y=element_blank()) + scale_fill_discrete(name = "Correct")
time$rsgn <- factor(time$rsgn, labels=c("r -","r +"))
tm <- summarise(group_by(time, correct, plot, rsgn), m=mean(time))
t1 <- ggplot(data=subset(time, correct==0), aes(x=time)) + geom_histogram(binwidth=0.5) + 
  geom_vline(data=subset(tm, correct==0), aes(xintercept = m), color="red") +
  facet_grid(plot~rsgn) + labs(title="Did not detect", x="Log(Time) Taken", y=element_blank())  
t2 <- ggplot(data=subset(time, correct==1), aes(x=time)) + geom_histogram(binwidth=0.5) + 
  geom_vline(data=subset(tm, correct==1), aes(xintercept = m), color="red") +
  facet_grid(plot~rsgn) + labs(title="Detected", x="Log(Time) Taken", y=element_blank())  
grid.arrange(t1, t2, ncol=2, top = "Log(Time) by plot design, true plot correlation and detection")
@
  \label{time} 
  \caption{Histograms of log time taken to make a decision. r+ and r- indicate the sign of true plot correlation. The vertical red line is the average time of the particular group. On average scatter plots are faster and the true plot is detected more often, with r-.}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
<<confidence, dependson='time', fig.width=6, fig.height=6, out.width='0.7\\textwidth', echo=FALSE, error=FALSE, message=FALSE, warning=FALSE>>=
conf <- data.frame(plot=full$plot, conf=full$conf_level, correct=full$correct, rsgn=full$sign)
conf$rsgn <- factor(conf$rsgn, labels=c("r -","r +"))
cm <- summarise(group_by(conf, correct, plot, rsgn), m=mean(conf))
c1 <- ggplot(data=subset(conf, correct==0), aes(x=conf)) + geom_histogram(binwidth=1) + 
  geom_vline(data=subset(cm, correct==0), aes(xintercept = m), color="red") +
  facet_grid(plot~rsgn) + labs(title="Did not detect", x="Confidence", y=element_blank())  
c2 <- ggplot(data=subset(conf, correct==1), aes(x=conf)) + geom_histogram(binwidth=1) + 
  geom_vline(data=subset(cm, correct==1), aes(xintercept = m), color="red") +
  facet_grid(plot~rsgn) + labs(title="Detected", x="Confidence", y=element_blank())  
grid.arrange(c1, c2, ncol=2, top = "Confidence by plot design, true plot correlation and detection")
@
  \label{confidence} 
  \caption{Histograms of reported confidence levels. 1 - Low, 5 - High. Detection had a minor detrimental impact on confidence, whilst time taken increased it. There was no statistically significant difference on confidence level between plot designs.}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
<<confidence2, dependson='time', fig.width=6, fig.height=6, out.width='0.7\\textwidth', echo=FALSE, error=FALSE, message=FALSE, warning=FALSE>>=
full$subj_id <- factor(full$ip_address, labels=1:207)
y <- data.frame(table(full$subj_id))
keep2 <- y$Var1[y$Freq>9]
sub <- filter(full, subj_id %in% keep2)
sub <- select(sub, conf_level, correlation, test_param, smoothed, n, correct, sign, plot, subj_id) #c(7, 15, 16, 17, 20, 27)]
#sub <- summarise(group_by(sub, subj_id), correct = sum(correct), conf=mean(conf_level))
#sub <- merge(sub, y, by.x="subj_id", by.y="Var1")
#sub <- mutate(sub, prop = correct/Freq)
qplot(correlation, 6-conf_level, data=sub, alpha=I(0.1)) + 
  geom_smooth(method="loess") + 
  facet_grid(n~plot+smoothed) +
  labs(x = "Correlation", y = "Confidence (5=High, 1=Low)")
@
  \label{confidence2}
  \caption{Individual subject accuracy versus subject average confidence. There does not appear to be any relationship between the two.}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
<<pins, dependson='samplesize', fig.width=6, fig.height=10, out.width='0.7\\textwidth', echo=FALSE, error=FALSE, message=FALSE, warning=FALSE>>=
# correl <- read.csv("correlations.csv") # You have already read this
count.setup <- select(full, pic_id, response_0, actual_location, 
              test_param, smoothed, n)
count.setup$response_0 <- as.character(count.setup$response_0) #full[,c(5, 6, 10, 15, 16, 17)]
# Need to use the tidyr commands instead of cSplit
# Here's where we will need to make some changes to incorporate the multiple picks
#pin <- pin %>% transform(response_0= strsplit(as.character(response_0), ",")) %>% unnest(response_0)
#pin$response_0 <- separate(pin, response_0, "response_0", sep=",", extra="drop")
count.setup$choice <- separate(count.setup, response_0, c("choice", "l1", "l2"), ",", extra="drop")$choice
count.setup$choice[str_detect(count.setup$actual_location, count.setup$response_0)] <- 
  count.setup$actual_location[str_detect(count.setup$actual_location, count.setup$response_0)]
                         #as.integer(pin$response_0)
counts <- data.frame(table(count.setup$pic_id, count.setup$choice))
counts$Var1 <- as.numeric(as.character(counts$Var1))
counts$Var2 <- as.numeric(as.character(counts$Var2))
colnames(counts) <- c("lineup", "plot", "count")
pin <- merge(counts, Turk[-19], by.x="lineup", by.y="pic_id")
pin <- select(pin, lineup, plot, count, smoothed, true_pos, n, test_param, r, attempt)#pin[,c(1, 2, 3, 12, 13, 15, 11, 20)]
pin$r <- factor(pin$r)
colnames(pin) <- c("lineup", "plot", "count", "smoothed", "true_pos", "n", "design", "r", "attempt")
pin <- mutate(pin, design=ifelse(design=="scatter", "Scatterplot", "Overlaid Lines"))#, smoothed=ifelse(smoothed=="no", 0, 1))
pin$base <- 0
pin$Correlation <- diag(as.matrix(correl[pin$lineup, (pin$plot+2)]))
pin <- mutate(pin, true = ifelse(plot==true_pos, "True plot", "Null plot"), percent = count/attempt)
#pin <- merge(pin, Turk[,c(2, 16)], by.x = "lineup", by.y = "pic_id")
pin.a <- ggplot(data=filter(pin, smoothed==0 & design == "Scatterplot")) + geom_errorbar(aes(x=Correlation, ymin=base, ymax=percent, colour=true)) +
       geom_point(aes(x=Correlation, y=percent, colour=true)) + coord_fixed() + facet_grid(n~r) + labs(title="Unsmoothed Scatterplot", y="Percent Chosen") + theme(legend.position="none")
pin.b <- ggplot(data=subset(pin, smoothed==1 & design == "Scatterplot")) + geom_errorbar(aes(x=Correlation, ymin=base, ymax=percent, colour=true)) +
  geom_point(aes(x=Correlation, y=percent, colour=true)) + coord_fixed()  + facet_grid(n~r) + labs(title="Smoothed Scatterplot", y="Percent Chosen") + theme(legend.position="none")
pin.c <- ggplot(data=subset(pin, smoothed==0 & design == "Overlaid Lines")) + geom_errorbar(aes(x=Correlation, ymin=base, ymax=percent, colour=true)) +
  geom_point(aes(x=Correlation, y=percent, colour=true)) + coord_fixed()  + facet_grid(n~r) + labs(title="Unsmoothed Overlaid Lines", y="Percent Chosen") + theme(legend.position="none")
pin.d <- ggplot(data=subset(pin, smoothed==1 & design == "Overlaid Lines")) + geom_errorbar(aes(x=Correlation, ymin=base, ymax=percent, colour=true)) +
  geom_point(aes(x=Correlation, y=percent, colour=true)) + coord_fixed()  + facet_grid(n~r) + labs(title="Smoothed Overlaid Lines", y="Percent Chosen") + theme(legend.position="none")
grid.arrange(pin.a, pin.b, pin.c, pin.d, ncol=1)
@
